---
title: "p8105_hw3_yz4187"
author: "Yiwen Zhao"
date: "10/19/2021"
output: github_document
---

```{r, echo = FALSE, message = FALSE}
library(tidyverse)
library(p8105.datasets)
```

### Problem1

*The goal is to do some exploration of this dataset. To that end, write a short description of the dataset, noting the size and structure of the data, describing some key variables, and giving illstrative examples of observations. Then, do or answer the following (commenting on the results of each):*

```{r, eval=FALSE}
instacart = p8105.datasets::instacart %>% 
  janitor::clean_names()

data("instacart")
skimr::skim(instacart)
```

**Description:**
This dataset named "instacart" contains 1384617 rows and 15 columns. It contains 4 character variables and 11 numeric variables. There are key variables such as "eval_set", "product_name", "aisle", "department". Except these four variables, all other variables are numeric.

#### Questions:
*Question: How many aisles are there, and which aisles are the most items ordered from?*
```{r aisle and order}
instacart %>% 
  group_by(aisle) %>% 
  count(aisle) %>%
  arrange(desc(n))
```
**Answer:** There are 134 aisles. "Fresh vegetables" are the most items are order from .

*Question: Make a plot that shows the number of items ordered in each aisle, limiting this to aisles with more than 10000 items ordered. Arrange aisles sensibly, and organize your plot so others can read it.*

```{r make a plot}
instacart_plot = instacart %>%
  count(aisle) %>%
  filter(n >= 10000) %>%
  arrange(desc(n)) %>%
  mutate(aisle = forcats::fct_reorder(aisle, n))

  ggplot(instacart_plot, aes(x = aisle, y = n)) + geom_bar(stat = "identity") +
  labs(
    title = "Number of Items Ordered in Each Aisle",
    x = "Aisle",
    y = "Number of Orders",
    caption = "Data from the Instacart Dataset"
  ) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

*Question: Make a table showing the three most popular items in each of the aisles “baking ingredients”, “dog food care”, and “packaged vegetables fruits”. Include the number of times each item is ordered in your table.*

```{r table showing three most popular items, message=FALSE}
instacart %>%
  filter(aisle %in% c("baking ingredients","dog food care","packaged vegetables fruits")) %>%
  group_by(aisle, product_name) %>% 
  summarize(n = n()) %>% 
  filter(n == max(n)) %>% 
  arrange(desc(n)) %>%
  knitr::kable()
```

*Question: Make a table showing the mean hour of the day at which Pink Lady Apples and Coffee Ice Cream are ordered on each day of the week; format this table for human readers (i.e. produce a 2 x 7 table).*

```{r table showing mean hour, message=FALSE}
instacart %>%
  filter(product_name %in% c("Pink Lady Apples","Coffee Ice Cream"))  %>%
  select(product_name, order_dow, order_hour_of_day) %>% 
  group_by(product_name, order_dow) %>% 
  summarize(mean_hour = mean(order_hour_of_day)) %>%
  spread(key = order_dow, value = mean_hour) %>% 
  rename("Product Name" = "product_name", "Saturday" = "6", 
         "Sunday" = "0", "Monday" = "1", "Tuesday" = "2", 
         "Wednesday" = "3", "Thursday" = "4", "Friday" = "5") %>%
  knitr::kable()
```


### Problem 2

*First, do some data cleaning:*

include only responses from “Excellent” to “Poor”
organize responses as a factor taking levels ordered from “Poor” to “Excellent”

```{r}
brfss_data =
  brfss_smart2010 %>% 
  janitor::clean_names() %>% 
  filter(topic == "Overall Health") %>% 
  mutate(response = fct_relevel(response, c("Poor", "Fair", "Good", "Very good", "Excellent"))) %>%
  arrange(response)
```

*Using this dataset, do or answer the following (commenting on the results of each):*
#### Questions:

*Question: In 2002, which states were observed at 7 or more locations? What about in 2010?*
```{r}
brfss_data %>% 
  filter(year == 2002) %>% 
  group_by(year, locationabbr) %>%
  distinct(locationdesc) %>%
  count() %>%
  filter(n >= 7)

brfss_data %>% 
  filter(year == 2010) %>% 
  group_by(year, locationabbr) %>%
  distinct(locationdesc) %>%
  count() %>%
  filter(n >= 7)
```
**Answer:** In 2002, state CT,FL,MA,NC,NJ,PA were observed at 7 or more locations; in 2010, CA,CO,FL,MA,MD,NC,NE,NJ,NY,OH,PA,SC,TX,WA were observed at 7 or more locations.


*Question: Construct a dataset that is limited to Excellent responses, and contains, year, state, and a variable that averages the data_value across locations within a state. Make a “spaghetti” plot of this average value over time within a state (that is, make a plot showing a line for each state across years – the geom_line geometry and group aesthetic will help).*
```{r make a "spaghetti" plot, warning=FALSE}
brfss_plot = brfss_data %>% 
  select(year, locationabbr, locationdesc, response, data_value) %>%
  filter(response == "Excellent") %>%
  group_by(year, locationabbr) %>% 
  summarize(avg_value = mean(data_value))

ggplot(brfss_plot, aes(x = year, y = avg_value)) + geom_line(aes(color = locationabbr)) +
  labs(
    title = "Average Value over time within a state",
    x = "Year",
    y = "Average Value",
    caption = "Data from the BRFSS"
  ) 
```

*Question: Make a two-panel plot showing, for the years 2006, and 2010, distribution of data_value for responses (“Poor” to “Excellent”) among locations in NY State.*

```{r}
brfss_data %>% 
  filter(year %in% c(2006, 2010), 
         locationabbr == "NY",
         response %in% c("Poor","Fair","Good","Very good","Excellent")) %>% 
  group_by(year, response, data_value) %>%
  ggplot(aes(x = data_value)) + 
  geom_density(alpha = 0.4) + 
  facet_grid(~ year) +
  labs(
    title = "Distribution of data value for response in 2006 and 2010",
    x = "data value",
    y = "density",
    caption = "Data from the BRFSS"
  ) 
```

### Problem 3

*Load, tidy, and otherwise wrangle the data. Your final dataset should include all originally observed variables and values; have useful variable names; include a weekday vs weekend variable; and encode data with reasonable variable classes. Describe the resulting dataset (e.g. what variables exist, how many observations, etc).*
```{r}
accel_data = 
  read.csv("accel_data.csv") %>%
  janitor::clean_names() %>%
  mutate(weekday_vs_weekend = ifelse(day %in% c("Saturday", "Sunday"),"weekend", "weekday")) 
```
**Description:**
The Accelerometers dataset contains 35 rows and 1440 variables. Variables includes "week", "day_id", "day" and "activity 1- 1440".

*Traditional analyses of accelerometer data focus on the total activity over the day. Using your tidied dataset, aggregate accross minutes to create a total activity variable for each day, and create a table showing these totals. Are any trends apparent?*
```{r, warning=FALSE}
accel_table = 
  pivot_longer(
    accel_data,
    activity_1:activity_1440,
    names_to = "time",
    names_prefix = "activity_",
    values_to = "value"
  ) %>%
  mutate(time = as.integer(time)) %>%
  group_by(week, day_id) %>%
  summarise(total_value =  sum(value))
```
**Answer:** There is no particular trends apparent.

*Accelerometer data allows the inspection activity over the course of the day. Make a single-panel plot that shows the 24-hour activity time courses for each day and use color to indicate day of the week. Describe in words any patterns or conclusions you can make based on this graph.*
```{r, warning=FALSE}
accel_data %>%
  pivot_longer(
    activity_1:activity_1440,
    names_to = "time",
    names_prefix = "activity_",
    values_to = "value"
  ) %>%
  mutate(time = as.integer(time)) %>%
  group_by(day_id, day) %>%
  ggplot(
    aes(x = time, y = value, color = day)
  ) +
  geom_line() +
  scale_x_discrete(
    limits = c(0:1440),
    breaks = c(1,241,481,721,961,1201,1440), 
    labels = c("00","04","08","12","16","20","24")) + 
  labs(
    title = "24-hour activity for each day",
    x = "Hour",
    y = "Hour Activity",
    caption = "Data from the Accelerometers Dataset"
  ) 
```

**Description:** According to the graph, the most activities happened between 8-10p.m., and there is not many activities during 0-5 a.m.. We can also find that the most activities happened on Fridays.
